Correlation among smart grid actors

### 2015-05-12 Article.tex
update

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Abstract
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

\end{abstract}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Abstract
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Achieving a successful energetic transition became a major goal for the 21st century in most developped countries. The reconciliation of several research areas and their recent focus on the same smart grid objective has led to major technical improvements. For instance, allowing large penetrations of renewables into the electricity production seemed more like a dream yesterday, but appears more and more doable as research progresses. The inherent volatility of some of these energy sources poses indeed various problems in such a constrained environment. It is often supposed that a large number of these small generators will be decentralized down to the distribution networks and even be owned by individuals. By enabling bi-directional flows, this vision revolutionises the nature of the simple todays's consumer into some futuristic agent that both consumes and produces. It is often considered that these individual productions will be used only to meet the agent own demand (in real time or through batteries).

In this paper, we consider agents that tend to produce more than they consume and seek to sell their surplus of production. More precisely, we rely on aggregations of these agents that can be seen as virtual power plants with production and consumption components that are both variable. Because these virtual power plants are complex aggregations of different types of production means and consumption habits, the volatilities of the plants productions are deeply impacted by the correlation between the agents. We propose here an algorithm that takes the underlying correlation structure of the agents into account while forming the coalitions. We show then that the resulting diversified coalitions are able to generate higher benefits on a constrained energy market, and are more resilient to random failures of the agents.
\end{abstract}
